Adopting agile in the large: motivations, success factors and challenges

### 2013-10-29 journal/article.tex
Style update; added example bibliography
Some notes

\usepackage{multibib}
\newcites{gen}{References}
\usepackage{bibentry}

@@

\author{Kim Dikert, Maria Paasivaara, Casper Lassenius}

@@

\ead{kim-karol.dikert@aalto.fi, maria.paasivaara@aalto.fi, casper.lassenius@aalto.fi}

@@

--> Motivation for research
-- There are no systematic reviews for this
-- A collection of experience reports can be used for creating a theoretical
   base.

@@

RQ1 Why are transformations initiated?

RQ2 How do transformations proceed usually; do transformations exhibit patterns?

RQ3 What are typical successes and challenges in an large scale agile
    transformation process?

@@

--> Definition of large scale

@@

%\small
\fontsize{9pt}{10pt}\selectfont

\bibliographystyle{elsarticle-harv}
%\bibliographystyle{plain}
\bibliographystylegen{plain}

\bibliographygen{sources}

\nobibliography{sources_s}

\subsection*{Primary studies}

\begin{supertabular}{ l p{11.4cm} }
    {[}S1{]} & \bibentry{S1} \\  \shrinkheight{-1cm}
    {[}S2{]} & \bibentry{S2} \\ 
    {[}S3{]} & \bibentry{S3} \\ 
    {[}S4{]} & \bibentry{S4} \\ 
    {[}S5{]} & \bibentry{S5} \\ 
    {[}S6{]} & \bibentry{S6} \\ 
    {[}S7{]} & \bibentry{S7} \\ 
    {[}S8{]} & \bibentry{S8} \\ 
    {[}S9{]} & \bibentry{S9} \\
    {[}S10{]} & \bibentry{S10} \\ 
    {[}S11{]} & \bibentry{S11} \\ 
    {[}S12{]} & \bibentry{S12} \\  \shrinkheight{-3cm}
    {[}S13{]} & \bibentry{S13} \\ 
    {[}S14{]} & \bibentry{S14} \\ 
    {[}S15{]} & \bibentry{S15} \\ 
    {[}S16{]} & \bibentry{S16} \\ 
    {[}S17{]} & \bibentry{S17} \\ 
    {[}S18{]} & \bibentry{S18} \\ 
    {[}S19{]} & \bibentry{S19} \\ 
    {[}S20{]} & \bibentry{S20} \\ 
    {[}S21{]} & \bibentry{S21} \\ 
    {[}S22{]} & \bibentry{S22} \\ 
    {[}S23{]} & \bibentry{S23} \\ 
    {[}S24{]} & \bibentry{S24} \\ 
    {[}S25{]} & \bibentry{S25} \\ 
    {[}S26{]} & \bibentry{S26} \\ 
    {[}S27{]} & \bibentry{S27} \\ 
    {[}S28{]} & \bibentry{S28} \\ 
    {[}S29{]} & \bibentry{S29} \\ 
    {[}S30{]} & \bibentry{S30} \\ 
\end{supertabular}\end{document}

>>>>

% Multiple bibliographies
%\usepackage{multibib}
%\newcites{gen}{References}
%\usepackage{bibentry}

@@

\author{Kim Dikert}
\ead{kim-karol.dikert@aalto.fi}

\author{Maria Paasivaara}
\ead{maria.paasivaara@aalto.fi}

\author{Casper Lassenius}
\ead{casper.lassenius@aalto.fi}

@@

@@

--> Motivation for research
-- There are no systematic reviews for this
-- A collection of experience reports can be used for creating a theoretical
   base.
--> There is interest in large scale [ref XP13 workshop]

--> Why is large scale software development different from smaller scale?

@@

\begin{itemize}

\item
RQ1: Why are transformations initiated?

\item
RQ2: How do transformations proceed usually; do transformations exhibit patterns?

\item
RQ3: What are typical successes and challenges in an large scale agile
    transformation process?

\end{itemize}

@@

A key question in the study was the definition of \emph{large scale}.
--> Ref: the XP conference

@@

\bibliographystyle{elsarticle-harv}
%\bibliographystylegen{plain}

\bibliography{sources_background}

\end{document}
